Surrogate Modelling of the Tritium Breeding Ratio

### 2020-05-14 elevator_pitch/elevator_pitch.tex
add a bit about smaller models
remove page number, adjust margins
Edits to elevator pitch

\usepackage[margin=2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

@@

\title{Surrogate Modelling of the Tritium Breeding Ratio}
\date{2020\\ January -- April}
\author{
	Graham Van Goffrier, University College London\\
	\and Petr Mánek, University College London
}

@@

\maketitle

@@

Having implemented and deployed our sampling software on a high performance cluster, we
used the MC TBR model to generate over~$9\cdot 10^5$ datapoints for training and
test purposes. On this set, we investigated possibilities for
dimensional reduction using Principal Component Analysis, Kriging and
autoencoders, and concluded that no straightforward reduction was possible
without significant information loss. We reviewed 9~families of surrogate models for potential
applicability, benchmarked their behaviour as a function of training set size and tuned their
hyperparameters via Bayesian Optimisation.

Here we present the
performance and scaling properties of these
models, the fastest of which, an artificial neural network,
demonstrated~$R^2=\num{0.985}$ and a mean
prediction time of~$\SI{0.898}{\micro\second}$, representing a relative speedup of $8\cdot 10^6$
with respect to the expensive MC TBR model. We further present a novel adaptive
sampling algorithm, Quality-Adaptive Surrogate Sampling, capable
of interfacing with any of the individually studied surrogates. Our preliminary
testing on a toy TBR theory has demonstrated the efficacy of this algorithm for
accelerating the surrogate modelling process.

>>>>

\usepackage[left=2.5cm,right=2.5cm,top=1cm,bottom=1cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}

@@

\title{Surrogate Modelling of the Tritium Breeding Ratio}
\date{2020\\ January -- April}
\author{
	Petr Mánek, University College London\\
	\and Graham Van Goffrier, University College London
}

@@

\maketitle
\thispagestyle{empty}

@@

Having implemented and deployed our sampling software on a high performance cluster, we
used the MC TBR model to generate over~\num{900000} datapoints for training and
test purposes. On this set, we investigated possibilities for
dimensional reduction using Principal Component Analysis, variograms and
autoencoders, and concluded that no straightforward reduction was possible
without significant information loss. We reviewed 9~families of surrogate models for potential
applicability, benchmarked their behaviour as a function of training set size and tuned their
hyperparameters via Bayesian Optimisation.

Here we present the performance and scaling properties of these
models, the fastest of which, an artificial neural network,
demonstrated~$R^2=\num{0.985}$ and a mean
prediction time of~$\SI{0.898}{\micro\second}$, representing a relative speedup of $8\cdot 10^6$
with respect to the expensive MC TBR model. While this surrogate was trained on
a set of size~\num{500000}, we demonstrated that comparable results can also be
achieved using only~\num{10000} datapoints. We further present a novel adaptive
sampling algorithm, Quality-Adaptive Surrogate Sampling, which applies Markov chain Monte Carlo methods to probe high-error regions of the surrogate during training, and is capable
of interfacing with any of the individually studied surrogates. Our preliminary
testing on a toy TBR theory has demonstrated the efficacy of this algorithm for
accelerating the surrogate modelling process.
